Model Recognition as Planning

### 2018-10-24 doc/icaps-19/model-recognition.tex

  (:action inc-y-even
    :parameters (?y1 ?y2)
    :precondition (and (ycoord ?y1) (next ?y1 ?y2) (q0))
    :effect (and (not (ycoord ?y1)) (ycoord ?y2)
                 (not (q0)) (q1))

  (:action inc-y-odd
    :parameters (?y1 ?y2)
    :precondition (and (ycoord ?y1) (next ?y1 ?y2) (q1)))
    :effect (and (not (ycoord ?y1)) (ycoord ?y2)
                 (not (q1)) (q0)))

>>>>

  (:action inc-y-even
    :parameters (?y1 ?y2)
    :precondition (and (ycoord ?y1) (next ?y1 ?y2) (q0))
    :effect (and (not (ycoord ?y1)) (ycoord ?y2)
                 (not (q0)) (q1)))

  (:action inc-y-odd
    :parameters (?y1 ?y2)
    :precondition (and (ycoord ?y1) (next ?y1 ?y2) (q1))
    :effect (and (not (ycoord ?y1)) (ycoord ?y2)
                 (not (q1)) (q0)))
